### 2019-03-07 manuscript/main.tex
- fixing affiliations as requested by Will and Itay - fixed maddison_2007 citation

% Accumulate ideas for titles here...
%
% When your favorite trait is not enough to explain diversification: An example of diversification linked to polyploidy and breeding system in Solanaceae % E: Fun, but I think we need something more formal
%
% New comparative approaches for the study of breeding system, polyploidy, and lineage diversification % E: the tentative title given to New Phyt
%
% Comparative study of breeding system, ploidy, and lineage diversification % E: too boring?
%
% Interacting effects of ploidy and breeding system on lineage diversification % E: but "effects" is too causal

\begin{center}
    \textbf{Interacting associations between ploidy, breeding system, and lineage diversification}
\end{center}

@@

\noindent
Rosana Zenil-Ferguson,%
\endnote{University of Minnesota Twin Cities}
%
\noindent
J.~Gordon Burleigh,%
\endnote{University of Florida}
%
\noindent
William A.~Freyman,%
\endnote{23 and me}
%
\noindent
Boris Igi\'c,%
\endnote{University of Illinois}
%
\noindent
Itay Mayrose,%
\endnote{Tel Aviv University}
%
and
Emma E.~Goldberg%
\endnote{University of Minnesota Twin Cities}

\theendnotes

\noindent
Author for correspondence: Rosana Zenil-Ferguson

\noindent
\textit{Running head:} Ploidy and breeding systems in Solanaceae
% E: I've been changing "polyploidy" to "ploidy" in various places because "polyploidy" is one state of the "ploidy" trait, just as "SI" is one state of the "breeding system" trait

@@

NSF DEB-1655478.
The Minnesota Supercomputing Institute (MSI) at the University of Minnesota provided computing resources for this project.

>>>>

% Accumulate ideas for titles here...
%
% When your favorite trait is not enough to explain diversification: An example of diversification linked to polyploidy and breeding system in Solanaceae % E: Fun, but I think we need something more formal
%
%% When the favorite trait is not enough: the link of polyploidy and breeding system in diversification %B: <- eh?
%
% New comparative approaches for the study of breeding system, polyploidy, and lineage diversification % E: the tentative title given to New Phyt
%
% Comparative study of breeding system, ploidy, and lineage diversification % E: too boring?
%
% Interacting effects of ploidy and breeding system on lineage diversification % E: but "effects" is too causal
%
%B: associations isn't exactly right; I think it somewhat undermines the causality from DP to IC; anyway, it's not particularly bad.
%
%% Interaction of ploidy and breeding system in lineage diversification %B: <- how 'bout that?
%
\begin{center}
    \textsc{Interacting associations between ploidy, breeding system, and lineage diversification}

@@

\noindent
Rosana Zenil-Ferguson$^{1,\dagger}$,
%
\noindent
J.~Gordon Burleigh$^{2}$,
%
\noindent
William A.~Freyman$^{1}$,
%
\noindent
Boris Igi\'c$^{3}$,
%
\noindent
Itay Mayrose$^{4}$,
%
and
Emma E.~Goldberg$^{1}$
%
\end{center}

%
\noindent$^{1}$Department of Ecology, Evolution, and Behavior, University of Minnesota, Saint Paul, MN 55108, U.S.A.\\
\noindent$^{2}$Department of Biology, University of Florida, Gainesville, FL 32611, U.S.A.\\
\noindent$^{3}$Department of Biological Sciences, University of Illinois at Chicago, Chicago, IL 60607, U.S.A. \\
\noindent$^{4}$School of Plant Sciences and Food Security, Tel Aviv University, Tel Aviv 6997801, Israel.\\
\noindent$^\dagger$\textit{Author for correspondence}.\\
\vfill
\noindent\textit{Running head:} Ploidy and Breeding Systems in Solanaceae
%\vfill

@@

%B: Perhaps other's funding sources for max BSF/NSF payoff? I added ours; no harm, I presume.
NSF DEB-1655692 to BI, and DEB-1655478 to EEG.
The Minnesota Supercomputing Institute (MSI) at the University of Minnesota provided computing resources for this project.
